\documentclass{amsart}
\setcounter{tocdepth}{3}
\setcounter{secnumdepth}{3}

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{eucal}
\usepackage{tikz-cd}
\usepackage{pdfsync}
\usepackage{relsize}
\usepackage{afterpage}

\usepackage[unicode=true, pdfusetitle,
 bookmarks=true,bookmarksnumbered=false,
 breaklinks=false,
 backref=false,
 colorlinks=true,
 %linkcolor=blue!70!black,
 citecolor=black,
 urlcolor=blue!78!red,
 final
]{hyperref}

\usepackage[capitalise]{cleveref}

\usepackage[color=orange!80,bordercolor=black,textwidth=3cm,textsize=small,colorinlistoftodos]{todonotes}
\makeatletter \providecommand\@dotsep{5}
\makeatother
\newcommand{\amsartlistoftodos}{\makeatother \listoftodos\relax}

\newenvironment{eq}{\begin{equation}}{\end{equation}}
\newenvironment{eq*}{\begin{equation*}}{\end{equation*}}

\numberwithin{equation}{section}

\newtheorem{thm}[equation]{Theorem}
\newtheorem{prop}[equation]{Proposition}
\newtheorem{lem}[equation]{Lemma}
\newtheorem{cor}[equation]{Corollary}

\newtheoremstyle{example}{\topsep}{\topsep}{}{}{\bfseries}{.}{2pt}{\thmname{#1}\thmnumber{ #2}\thmnote{ #3}}
\theoremstyle{example}

\newtheorem{nota}[equation]{Notation}
\newtheorem{example}[equation]{Example}
\newtheorem{defn}[equation]{Definition}
\newtheorem{rem}[equation]{Remark}
\newtheorem{comment}[equation]{Comment}

%% E.P. notes
\newcommand{\epnote}[1]{\todo[color=blue!40,linecolor=blue!40!black,size=\tiny]{#1}}
\newcommand{\epmpar}[1]{\todo[noline,color=blue!40,linecolor=blue!40!black,size=\tiny]{#1}}
\newcommand{\epnoteil}[1]{\todo[inline,color=blue!40,linecolor=blue!40!black,size=\normalsize]{#1}}

%% N.G. notes
\newcommand{\ngnote}[1]{\todo[color=red!40,linecolor=red!40!black,size=\tiny]{#1}}
\newcommand{\ngmpar}[1]{\todo[noline,color=red!40,linecolor=red!40!black,size=\tiny]{#1}}
\newcommand{\ngnoteil}[1]{\todo[inline,color=red!40,linecolor=red!40!black,size=\normalsize]{#1}}

% Cleveref definitions
\crefname{prop}{Proposition}{Propositions}
\crefname{thm}{Theorem}{Theorems}
\crefname{defn}{Definition}{Definitions}
\crefname{notn}{Notation}{Notations}
\crefname{construction}{Construction}{Constructions}
\crefname{lem}{Lemma}{Lemmas}
\crefname{rem}{Remark}{Remarks}
\crefname{cor}{Corollary}{Corollaries}
\crefname{scholium}{Scholium}{Scholia}
\crefname{figure}{Figure}{Figures}
\crefname{equation}{Display}{Displays}
\crefname{eq}{Display}{Displays}
\crefname{eqn}{Display}{Displays}

\newcommand{\quotient}[2]{{\raisebox{.2em}{$#1$}\left/\raisebox{-.2em}{$#2$}\right.}}



\title[Classification of 3-groups]{Action operads, free algebras on invertible objects, and the classification of 3-groups} 
\author{Edward G. Prior}

\begin{document}

\begin{titlepage}
\maketitle
\pagenumbering{gobble}
\end{titlepage}

\pagenumbering{arabic}

\tableofcontents
\pagebreak

\input{actionoperad.tex} 

\input{initialalgebra.tex} 

\input{coeqalgebra.tex}

\input{2groupclass.tex}

\input{cohomology.tex}

\input{3groupclass.tex}



\begin{thebibliography}{9}

\bibitem{hda5}
John C. Baez; Aaron D. Lauda.
\textit{Higher-Dimensional Algebra V: 2-Groups}.
https://arxiv.org/pdf/math/0307200.pdf 

\bibitem{picard}
K. H. Ulbrich
\textit{Group cohomology for Picard categories}
Journal of Algebra, 91 (1984), pp. 464-498 
http://dx.doi.org/10.1016/0021-8693(84)90114-5

\bibitem{kkg}
K. H. Ulbrich
\textit{Kohärenz in Kategorien mit Gruppenstruktur}
Journal of Algebra, 72 (1981), pp. 279-295
http://dx.doi.org/10.1016/0021-8693(81)90295-7

\bibitem{graphicalmon}
Peter Selinger.
\textit{A survey of graphical languages for monoidal categories}.
http://www.mscs.dal.ca/~selinger/papers/graphical.pdf

\bibitem{operadborel} 
Nick Gurski. 
\textit{Operads, tensor products, and the categorical Borel construction}. 
 arXiv:1508.04050 [math.CT].

\bibitem{bct}
Tom Leinster.
\textit{Basic Category Theory}
Cambridge Studies in Advanced Mathematics, Vol. 143, Cambridge University Press, Cambridge, 2014.
https://arxiv.org/pdf/1612.09375v1.pdf

\bibitem{eckhil}
Eckmann, B.; Hilton, P. J. 
\textit{Group-like structures in general categories. I. Multiplications and comultiplications}
Mathematische Annalen, 145 (3), pp. 227–255

\end{thebibliography}

\end{document}